Replication of Brydevall et al. 2018

### 2024-07-10 219-2023-analysis/manuscript.qmd
cleanup quarto headers

```{r}
#| label: Load libraries
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: Get preprocessed data from OSF
#| include: false
#| echo: false

@@

```{r}
#| label: Load the Behavioral Data
#| echo: false
#| message: false

@@

```{r}
#| label: Compute RPEs and IPEs
#| echo: false
#| message: false

@@

```{r}
#| label: Load EEG data
#| echo: false
#| message: false

@@

```{r}
#| label: Merge RPE and IPE info into EEG data
#| echo: false
#| message: false

@@

```{r}
#| label: Count usable segments for RPEs
#| echo: false
#| message: false

@@

```{r}
#| label: Count usable segments for IPEs
#| echo: false
#| message: false

@@

```{r}
#| label: Exclude bad EEG
#| echo: false

@@

```{r}
#| label: Generate data for Grand Averages
#| echo: false
#| message: false

@@

```{r}
#| label: Difference wave summary data
#| echo: false
#| message: false

@@

```{r}
#| label: Compute ANOVA data
#| echo: false
#| message: false

@@

>>>>

```{r}
#| label: Load libraries
#| include: false

@@

```{r}
#| label: Get preprocessed data from OSF
#| include: false

@@

```{r}
#| label: Load the Behavioral Data
#| include: false

@@

```{r}
#| label: Compute RPEs and IPEs
#| include: false

@@

```{r}
#| label: Load EEG data
#| include: false

@@

```{r}
#| label: Merge RPE and IPE info into EEG data
#| include: false

@@

```{r}
#| label: Count usable segments for RPEs
#| include: false

@@

```{r}
#| label: Count usable segments for IPEs
#| include: false

@@

```{r}
#| label: Exclude bad EEG
#| include: false

@@

```{r}
#| label: Generate data for Grand Averages
#| include: false

@@

```{r}
#| label: Difference wave summary data
#| include: false

@@

```{r}
#| label: Compute ANOVA data
#| include: false

@@

### Exploratory Analysis

Question: What if we run a model that includes both IPE and RPE as predictors to account for the fact that we have overlapping manipulations. And what if we include the magnitude of the prediction error rather than just presence/absence?

```{r}
#| include: false
trial.level.data <- data.eeg.filtered.rpe.ipe %>%
  filter(t %in% frn.window, subject %in% ipe.good.subjects) %>%
  group_by(subject, electrode, hand_id, card_id, ipe, rpe) %>%
  summarize(M = mean(v))
```

```{r}
#| message: false
library(lmerTest)
library(brms)

mm.result <- brm(M ~ rpe*electrode + ipe*electrode + (rpe + ipe + electrode | subject), data=trial.level.data)

summary(mm.result)
```

```{r}
library(broom.mixed)
rr <- ranef(mm.result, condVar=TRUE)
ff <- fixef(mm.result)
aa <- broom::augment(rr)

ggplot(aa,aes(estimate,level,xmin=lb,xmax=ub))+
  geom_errorbarh(height=0)+
  geom_vline(xintercept=0,lty=2)+
  geom_point()+facet_wrap(~variable,scale="free_x")
```

Question: Did the reward become less salient over time? Try splitting the data based on block and look at effect of RPE on FRN.

```{r}
trial.level.data.with.block <- data.eeg.filtered.rpe.ipe %>%
  filter(t %in% frn.window, subject %in% ipe.good.subjects) %>%
  group_by(subject, electrode, hand_id, card_id, ipe, rpe) %>%
  summarize(M = mean(v)) %>%
  mutate(block = if_else(hand_id <= 40, 0, 1))
```

```{r}
#| message: false
library(lmerTest)

mm.block.result <- lmer(M ~  rpe*block + electrode + (rpe*block + electrode | subject), data=trial.level.data.with.block)

summary(mm.block.result)
```
